A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-28 rr-flow.Rmd
addsection on related approaches closes #20

! TODO

>>>>

While this approach here was designed to scale well with the complexity of a computing-intense Project, we realise that this flexibility comes with a steep learning curve. A few packages are easing this burden for different parts of the workflow when this flexibility is not needed. The use of `rmarkdown` within a project, tracked with `git` can be simplified with the [workflowr-package](https://github.com/jdblischak/workflowr) [@workflowr]. The [drake-package](https://github.com/ropensci/drake) [@drake] is directly inspired by `make` and does only require knowledge in R, but can only handle dependencies within R. The [holepunch-package](https://karthik.github.io/holepunch/) [@holepunch] automizes the use of docker and uses [binder](https://mybinder.org) to move the analysis to the cloud so that no local installation of docker is required. It is well suited for simple analysis with low computational demands, because of memory and computing time limitations of binder. There are several alternatives to docker which fix the dependancies on R-packages. [packrat](https://rstudio.github.io/packrat/) [@packrat] is a way to fix package version via installing locally in the project, however it does not garuantees more then a fixed set of packages (Not R-version or system dependencies). Similar approaches are taken by [jetpack](https://github.com/ankane/jetpack) [@jetpack], [miniCRAN](https://cran.r-project.org/web/packages/miniCRAN/vignettes/miniCRAN-introduction.html) [@miniCRAN] and [checkpoint](https://cran.r-project.org/web/packages/checkpoint/vignettes/checkpoint.html) [@checkpoint]. Notable is also the package [`reprex`](https://github.com/tidyverse/reprex) [**repr**oducible **ex**ample, @reprex], but its scope is limited to small examples.

Another way to increase the chance of reproducibility is to develop an R-package for each analysis. The reasoning is that by abiding the strict rules of package development and specifieng all dependencies a high degree of stability can be archieved. This is approach is extensivly developed by @marwickPackagingDataAnalytical2018.
